### 2019-10-16 tim-lucas-model-ensembles.tex
Restructure intro.

%We need to switch to downscaling models
%But they have issues of low power.
%While prevalence points should not be primary data source, they should still be used.
%One way is ML.

@@

@@

Here we propose training a suite of level-zero machine learning models on point-level, binomial prevalence data and stacking these models with a polygon-level, Poisson incidence model.
This modelling scheme has similarities to previous stacking methods used for malaria mapping \citep{bhatt2017improved}.
However, as the response data in the level-zero models and the stacker are on different scales (prevalence is a proportion while incidence is a rate) there are a number of important differences.
Notably, we cannot simply take a weighted average of the predictions from the level-zero models; they need to be transformed to the incidence scale and some additional flexibility to allow for mispecification of this transform needs to be allowed.
To test the effectiveness of this approach we use data from four countries: Madagascar, Colombia, Indonesia and Senegal.
We train the machine learning models on both local and global data and examine a number of different combinations of covariates: just local or global machine learning predictions, or combining the two or combining local machine learning predictions with the raw environmental covariates.
While there isn't one consistently best model, we find that in nearly all cases, using some information from local machine learning models improves model performance.

@@

Table \ref{t:results} gives the correlation between observed and held out data (under random and spatially cross-validation) for models that use environmental covariates only, local machine learning models only and a combination of the two.
Many of the differences in performance are rather marginal.
Overall, in only one case (random cross-validation in Senegal) is Enviro the best performing model.
In two cases, Enviro perfoms equally well as another model: under spatially cross-validation in Senegal Enviro and Envir + ML\textsubscript{l} perform equally well, under random cross-validation in Colombia Enviro and ML\textsubscript{l} perform equally well.
Of the remaining six cases, in three cases ML\textsubscript{l} performs best and in three cases Envir + ML\textsubscript{l} performs best.
The greatest benefits in predictive performance occur under spatial cross validation and in the cases when the Enviro model is particularly poor.

>>>>

% New plan

% We need to do disaggregation but how do we do nonlinear

% We can do machine learning on prevalence and then combine...

% Stacking is a thing and has some nice theory.

% We found that it worked ok.

@@

Here we propose training a suite of level-zero machine learning models on point-level, binomial prevalence data and combining these predictions by using them as covariates in a polygon-level, Poisson incidence model.
This modelling scheme has similarities to previous stacking methods used for malaria mapping \citep{bhatt2017improved}.
However, as the response data in the level-zero models and the stacker are on different scales (prevalence is a proportion while incidence is a rate) there are a number of important differences.
Notably, we cannot simply take a weighted average of the predictions from the level-zero models; they need to be transformed to the incidence scale and some additional flexibility to allow for mispecification of this transform needs to be allowed.

@@

To test the effectiveness of the proposed approach we use data from four countries: Madagascar, Colombia, Indonesia and Senegal.
We train the machine learning models on both local and global data and examine a number of different combinations of covariates: just local or global machine learning predictions, or combining the two or combining local machine learning predictions with the raw environmental covariates.
While there isn't one consistently best model, we find that in nearly all cases, using some information from local machine learning models improves model performance.

@@

Table \ref{t:results} gives the correlation between observed and held out data (under random and spatially cross-validation) for models that use environmental covariates only, local machine learning models only and a combination of the two.
Many of the differences in performance are rather marginal.
Overall, in only one case (random cross-validation in Senegal) is Enviro the best performing model.
In two cases, Enviro perfoms equally well as another model: under spatially cross-validation in Senegal Enviro and Envir + ML\textsubscript{l} perform equally well, under random cross-validation in Colombia Enviro and ML\textsubscript{l} perform equally well.
Of the remaining five cases, in three cases ML\textsubscript{l} performs best and in two cases (random and spatial cross-validation in Indonesia) Envir + ML\textsubscript{l} performs best.
The greatest benefits in predictive performance occur under spatial cross-validation and in the cases when the Enviro model is particularly poor.
